`r params$doc_title`

### 2023-03-16 scripts/MSc.Rmd
small changes, dir structure

if (SAVE.files ==TRUE ){
  saveRDS(my_data_harm, paste0("../output/Rdata/", Sys.Date(), "_my_data_harm.rds"))
}

## load results from script `perform_mr.R`
est.bmi.gsd <- readRDS(dplyr::last(list.files("../output/Rdata/", pattern = "_est_BMI_GSD.rds", full.names = TRUE)))

@@

# read dat from "simstudy.R"  #------------------------------------------------
#est_sim <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_NSIM_", full.names = TRUE)))
# from "purrr-simstudy.R"
est_sim <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_purrr_NSIM_", full.names = TRUE)))
est_sim_architectures <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_architectures_purrr_NSIM_", full.names = TRUE)))
nsim <- nrow(est_sim)
```

>>>>

if (SAVE.files ==TRUE ){
  saveRDS(my_data_harm, paste0("../output/Rdata/harmonized-dat/", Sys.Date(), "_my_data_harm.rds"))
}

## load results from script `perform_mr.R`
est.bmi.gsd <- readRDS(dplyr::last(list.files("../output/Rdata/mr-results/", pattern = "_est_BMI_GSD.rds", full.names = TRUE)))

@@

# read dat from "simstudy.R"  #------------------------------------------------
#est_sim <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_NSIM_", full.names = TRUE)))
# from "purrr-simstudy.R"
est_sim <- readRDS(dplyr::last(list.files(path = "../output/Rdata/sim-results/", pattern = "_est_sim_purrr_NSIM_", full.names = TRUE)))
est_sim_architectures <- readRDS(dplyr::last(list.files(path = "../output/Rdata/sim-results/", pattern = "_est_sim_architectures_purrr_NSIM_", full.names = TRUE)))
nsim <- nrow(est_sim)
```
